{memer}: an R interface to the MEME Suite

### 2020-06-25 manuscript.Rmd
small edits

A key difference between `memer` and the MEME Suite tools is that `memer`
provides tools allowing the peak-level metadata to frame subsequent analysis.
For DNA ranges (such as in ChIP-seq), the `get_sequence()` utility acts as the
entrypoint to analysis with `memer`. `get_sequence()` returns a `Biostrings`
object containing the DNA sequence of each feature in the input ranges. If
ranges are split into groups by a metadata value, `get_sequence()` will return a
list of sequences for each group. When a sequence list is used as input into
`memer` core functions, the function will run once for each group, enabling a
native "split-apply-combine" workflow without any additional user overhead
\cite{splitapplycombine, whickham}. Together, these features empower users to
use range-based metadata as the centerpoint of their analyses.

### Discriminative analysis
A powerful feature of several MEME Suite Tools is the ability to perform
discriminative analysis, where motifs are identified or tested for enrichement
in one group of sequences relative to another. In many instances, running tools
in discriminative mode on a set of control sequences outperforms simply using
shuffled input sequences as the control (back this up, change wording?). Therefore, 
enabling complex discriminative analysis designs was central to the design of `memer`.

@@

>>>>

A key difference between `memer` and the MEME Suite tools is that `memer`
provides tools allowing the peak-level metadata to frame subsequent analysis.
For DNA ranges (such as in ChIP-seq), the `get_sequence()` utility acts as the
entrypoint to analysis with `memer`. `get_sequence()` returns a `Biostrings`
object containing the DNA sequence of each feature in the input ranges. If
ranges are split into groups by a metadata value, `get_sequence()` will return a
list of sequences for each group. When a sequence list is used as input into
`memer` core functions, the function will run once for each group, enabling a
native "split-apply-combine" workflow without any additional user overhead
\cite{splitapplycombine, wickham}. Together, these features empower users to
use range-based metadata as the centerpoint of their analyses.

### Discriminative analysis
A powerful feature of several MEME Suite Tools is the ability to perform
discriminative analysis, where motifs are identified or tested for enrichment
in one group of sequences relative to another. In many instances, running tools
in discriminative mode on a set of control sequences outperforms simply using
shuffled input sequences as the control (back this up, change wording? maybe:
using biologically relevant control sequences can improve quality of results?).
Therefore, enabling complex discriminative analysis designs was central to the
design of `memer`.

@@

## Metadata manipulation
 - `update_motifs()`
 - `force_best_match()`

## Data Visualization
 - tomtom best match
 - ame heatmaps by group
